---
title: "Eating Out"
author: "Kevin Ortega"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## There were two years in which the General Social Survey asked about the frequency of eating out. The variable name you are looking for is "eatout".
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
#source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(haven)
require(knitr)
require(foreign)
#library(haven)
```
```{r, eval=TRUE, WARNING=FALSE}
GSS <-read_dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

# Methods
  
Race is categorical 
  
Eating out is categorical

So we will use the CAT~CAT helper file.


```{r}
#mydata$race=revalue(mydata$race,=c("white","black","other")
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata, type="percent")

```

Races are white, black, and other the blue represents that eatout last week and the orange showswho didn't eat out. The bar chart shows that white people eat out the most.


```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```

The numerical results show that the white people ate out 83.11% of the time during a given week, and only 16.89% didn't.

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$eatout,mydata$race)
```
The chi square test shows that the p-value is 0.00002287 so we reject the null hypothesis since the p-value is lower than 0.05. 
The first fisher eact test
The Fisher exact test shows that the P-Value is much lower than 0.05 at 0.00721. Therefore we reject the null hypothesis. 
There is a difference between white and black, but no difference between black and other.